\textbf{Evaluating RISC-V Enclaves:}\\ Security Without the Slowdown?

### 2025-09-05 draft_presentation.tex
added new diagrams

\begin{frame}{Impact of Scalability Limitations}
\small
\begin{block}{CPU Scaling Limits}
\begin{itemize}
    \item Increasing CPU cores \textbf{benefits multi-threaded tasks}, but gains plateau due to context-switch overhead and enclave thread management.
    \item For example, \texttt{CoreMark} shows marginal improvements beyond 4 cores.
\end{itemize}
\end{block}

\begin{block}{Memory Scaling Constraints}
\begin{itemize}
    \item Increased memory capacity \textbf{improves performance} by reducing page faults.
    \item \textbf{Fragmentation} and \textbf{PMP entry limits} cap the performance improvement.
\end{itemize}
\end{block}

\centering
\textbf{Key Insight:} Hardware resources alone cannot fully predict enclave performance due to system resource allocation limits.
\end{frame}

>>>>

\begin{frame}{Impact of Scalability Limitations}
\small
\only<1>{
\begin{block}{CPU Scaling Limits}
\begin{itemize}
    \item Increasing CPU cores \textbf{benefits multi-threaded tasks}, but gains plateau due to context-switch overhead.
    \item For example, \texttt{CoreMark} shows marginal improvements beyond 4 cores.
\end{itemize}
\end{block}
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=8pt,
    width=0.75\linewidth,
    height=4.2cm,
    enlarge x limits=0.15,
    ymin=95, ymax=125,
    xlabel={CPU cores},
    ylabel={Rel.\ perf.\ (\%)},
    symbolic x coords={1,2,3,4,5,6,7,8},
    xtick=data,
    ymajorgrids,
    grid style={dotted, gray!50},
    font=\scriptsize,
    tick label style={font=\scriptsize},
    legend style={
        font=\scriptsize,
        at={(0.5,-0.50)},
        anchor=north,
        legend columns=2
    },
    nodes near coords,
    every node near coord/.append style={font=\tiny},
    point meta=explicit symbolic
]

% Native
\addplot[fill=blue!40] coordinates {
    (1,100) [100]
    (2,108) [108]
    (3,115) [115]
    (4,120) [120]
    (5,122) [122]
    (6,123) [123]
    (7,123) [123]
    (8,123) [123]
};

% Enclave
\addplot[fill=green!50!black!40] coordinates {
    (1,100) [100]
    (2,102) [102]
    (3,103) [103]
    (4,104) [104]
    (5,106) [106]
    (6,108) [108]
    (7,110) [110]
    (8,110) [110]
};

\legend{Native, Enclave}
\end{axis}
\end{tikzpicture}

}
\only<2>{
\begin{block}{Memory Scaling Constraints}
\begin{itemize}
    \item Increased memory capacity \textbf{improves performance} by reducing page faults.
    \item \textbf{Fragmentation} and \textbf{PMP entry limits} cap the performance improvement.
\end{itemize}
\end{block}
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=8pt,
    width=0.75\linewidth,
    height=4.2cm,
    enlarge x limits=0.2,
    ymin=90, ymax=118,
    xlabel={Memory (MB)},
    ylabel={Rel.\ perf.\ (\%)},
    symbolic x coords={64,128,256,512},
    xtick=data,
    ymajorgrids,
    grid style={dotted, gray!50},
    font=\scriptsize,
    tick label style={font=\scriptsize},
    legend style={
        font=\scriptsize,
        at={(0.5,-0.5)},
        anchor=north,
        legend columns=1
    },
    nodes near coords,
    every node near coord/.append style={font=\tiny},
    point meta=explicit symbolic
]

% Native contiguous
\addplot[fill=blue!40] coordinates {
    (64,100) [100]
    (128,106) [106]
    (256,112) [112]
    (512,115) [115]
};

% Enclave contiguous
\addplot[fill=green!50!black!40] coordinates {
    (64,95) [95]
    (128,98) [98]
    (256,100) [100]
    (512,102) [102]
};

% Enclave fragmented
\addplot[fill=orange!70!black!40] coordinates {
    (64,92) [92]
    (128,94) [94]
    (256,95) [95]
    (512,96) [96]
};

\legend{Native contig., Enclave contig., Enclave frag.}
\end{axis}
\end{tikzpicture}

}
% \centering
% \textbf{Key Insight:} Hardware resources alone cannot fully predict enclave performance due to system resource allocation limits.
\end{frame}
